\textbf{\sc Towards Deliberative Control in Marine Robotics}

### 2012-02-24 trunk/results.tex
[arch] moved synch failure example earlier in the text [result] reword paragraph about gulper in order to enlarge the motivation from simply Gulper to "sensor based" missions

A significant driver of the applicability of our work was the
implementation of MBARI's \emph{Gulper} water-samplers \cite{Bird07},
$2$ litre syringe style containers $10$ of which are encased within
the mid-body section of our Dorado vehicle as shown in Fig
\ref{fig:gulper}. However, the original design and intended use of
operation continued to dominated by a naive belief of collecting and
returning water samples as traditional ship-borne methods often
employ, namely using pre-scripted methods, albeit on a highly capable
robot. With the installation of \rx onboard the Dorado with its
capability to synthesize plans and replan on the fly, more imaginative
methods of sample acquisition were targeted.

@@

More interesting experiments are being carried out as a basis to track
more dynamic features such as ocean fronts \cite{fronts11} and
tracking more capable drifting platforms. In particular experiments
with a profiling CTD instrument, the \texttt{Wirewalker}
\cite{rainville01,pinkel11} are resulting in new modalities of making
Lagrangian and Eulerian observations. Fig. \ref{sep11-wirewalker}
shows one such experiment in September 2011 with a GPS-enabled
\texttt{Wirewalker} was tracked by the Dorado running \rx. We are
currently investigating spatio-temporal correlations \cite{gneiting07}
of CTD data obtained by the \texttt{Wirewalker} and tying it to the
observations made in the contextual environment by the Dorado's
sensors.

>>>>

A significant driver of the applicability of our work was the
growing need for AUVs mission to be driven by scientific sensor 
data.Thid trend is illustrated by the 
implementation of MBARI's \emph{Gulper} water-samplers \cite{Bird07},
$2$ litre syringe style containers $10$ of which are encased within
the mid-body section of our Dorado vehicle as shown in Fig
\ref{fig:gulper}. However, the original design and intended use of
operation continued to dominated by a naive belief of collecting and
returning water samples as traditional ship-borne methods often
employ, namely using pre-scripted methods, albeit on a highly capable
robot. With the installation of \rx onboard the Dorado with its
capability to synthesize plans and replan on the fly, more imaginative
methods of sample acquisition were targeted.

@@

More interesting experiments are being carried out as a basis to track
more dynamic features such as ocean fronts \cite{fronts11} and
tracking more capable drifting platforms. In particular experiments
with a profiling CTD instrument, the \texttt{Wirewalker}
\cite{rainville01,pinkel11} are resulting in new modalities of making
Lagrangian and Eulerian observations. Fig. \ref{fig:sept11-wirewalker}
shows one such experiment in September 2011 with a GPS-enabled
\texttt{Wirewalker} was tracked by the Dorado running \rxe. We are
currently investigating spatio-temporal correlations \cite{gneiting07}
of CTD data obtained by the \texttt{Wirewalker} and tying it to the
observations made in the contextual environment by the Dorado's
sensors.
